Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-02 hscc2017/paper.tex
Updated experiment.tar.gz URL
Moved experiment environment to cprover.org.

The median run-time for our benchmark set is $48$\,s, implying that \tool
can synthesize half of the controllers in less than one minute.  Overall,
the average synthesis time amounts to approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine for additional benchmarks, where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers were confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}\footnote{CBMC version: \url{https://github.com/diffblue/cbmc/archive/7a6cec1dd0eb8843559591105235f1f2c4678801.zip}}

>>>>

The median run-time for our benchmark set is $48$\,s, implying that \tool
can synthesize half of the controllers in less than one minute.  Overall,
the average synthesis time amounts to approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine for additional benchmarks, where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers were confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}}\footnote{CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
